# Data Analysis, Results, and Discussion: Longitudinal Tracking Phase


TODO: write intro section of this chapter


longitudinal study (cohort study)

Most of the results did not have statistical significance - but that's okay because this is exploratory research, which is inductive, rather than deductive.  https://youtu.be/URz4CAaJqnE


We were more interested in discovering interesting patterns.
We believe the findings from this study will lead to more confirmatory studies.

https://www.youtube.com/playlist?list=PLZp7Vke_WTVr8E4dM1fDeMJr2B7My9Gan

All statistical tests are two-tailed Mann-Whitney U test.

As the sample sizes were often small, the groups were imbalanced, and / or the data did not match the normality assumptions of parametric tests, we employed the non-parametric Mann-Whitney U test for all the null-hypothesis significance testing reported in this and the next chapter. This allows easy comparison between different categories of results.


Additionally, we also report Common Language Effect Size (CLES) for each statistical test result.
The common language effect size is the proportion of pairs where $x$ is higher than $y$. 
In other words, it is the probability that a score sampled at random from the first distribution will be greater than a score sampled from the second distribution. 
CLES was first introduced by McGraw and Wong (1992) [TODO]. The Python statistical library employed in data analysis -- Pingouin [@vallat2018pingouin] -- uses a brute-force version of the formula given by Vargha and Delaney 2000 [TODO]:
The advantage is of this method are twofold. First, the brute-force approach pairs each observation of x to its y counterpart, and therefore does not require normally distributed data. Second, the formula takes ties into account and therefore works with ordinal data.

<!-- In the interest of better presentation and readability of this chapter, more ancillary plots are presented in Appendices \@ref(app-plots-query) and \@ref(app-plots-search). -->



## Data Analysis Framework

<!----------- fig:data-analysis-framework ----------->
```{r data-analysis-framework, fig.scap='(ref:scap-data-analysis-framework)', fig.cap = '(ref:cap-data-analysis-framework)',  echo=FALSE, out.width='100%', fig.align='center'}
nbShowFig("figs/data-analysis-framework")
```
<!-- each text reference needs to be their own single paragraph ! -->
(ref:cap-data-analysis-framework) Data analysis framework followed in this dissertation.

(ref:scap-data-analysis-framework) Data analysis framework.

<!---- fig:data-analysis-framework (leave a blank line before this) ------>


This section describes the general framework for analysing the data collected in the *LongSAL* study.
It is described in Figure \@ref(fig:data-analysis-framework).


Here is the overall data analysis framework of my dissertation:
Two categories of data were collected from participants. 

1. Questionnaire data for individual differences: motivation, metacognition, self-regulation.
2. Search Log data containing URL visits, mouse events, webnavigation events, and the order and sequence of those events.

Questionnaire Data

1. Cleaning and Preprocessing
2. identifying user groups - latent profile analysis

Log Data

1. Log Data cleaning and pre-processing
2. URL categorization
3. Active Tab Identification
4. Higher levelSearch Behaviour Data Analysis framework - moves, tactics, strategies
5. Combining Latent Profiles with Search Behaviour Data

Trends Over Time
Difference Between Groups / Profiles
Entropy analysis of sequences









## Latent Profile Analysis {#sec-res-phase2-lpa}

<!----------- fig:lpa-profile-means ----------->
```{r lpa-profile-means, fig.scap='(ref:scap-lpa-profile-means)', fig.cap = '(ref:cap-lpa-profile-means)',  echo=FALSE, out.width='100%', fig.align='center'}
nbShowFig("figs/lpa-profile-means")
```
<!-- each text reference needs to be their own single paragraph ! -->
(ref:cap-lpa-profile-means) Mean Values of Indicator Variables for the two identified groups via Latent Profile Analysis (LPA). The grouping was based on the self-reported values of motivation (IMI), metacognition (MAI), self-regulation (SRQ), and a Memory Span task. 

(ref:scap-lpa-profile-means) Groups identified by Latent Profile Analysis.

<!---- fig:lpa-profile-means (leave a blank line before this) ------>


According to @ambrose2010howa, students' motivation, metacognition, and self-regulation are critical factors that determine, direct, and sustain what they do to learn.
<!-- their learning behaviors.  -->
Given our interest in understanding how these traits impact students' searching as learning behaviour, we collected self-perceived reports of all three constructs, via the IMI, MAI, and SRQ questionnaires (Section \@ref(sec-method-qsnr1)). 
However, it is important to note that these constructs are not single binary variables that can be used to easily group individuals. Rather, they are complex and multidimensional data that serve as observable indicators of a person's underlying latent characteristics.



To cluster participants into meaningful groups based on these multiple constructs, we turned to the educational psychology literature.
**Latent Profile Analysis (LPA)** is an increasingly popular statistical approach falling under the umbrella of person-centred techniques used in organizational psychology and child development research. It provides a framework for characterizing population heterogeneity in terms of differences across individuals on a set of behaviours or characteristics, as opposed to describing the variability of a single variable. By identifying latent subgroups within a population, LPA enables researchers to gain a more nuanced understanding of the complexity of human behaviour.


The person-centred approach underlying LPA is a departure from traditional variable-centred approaches such as multiple regression analysis. Instead of quantifying the role of particular variables in a study, LPA organizes a population into a finite number of mutually exclusive and exhaustive profiles, each comprising individuals who are similar to one another. In this way, LPA identifies distinct profiles of individuals who exhibit similar patterns of behaviour across multiple variables.


The identification and description of these latent profiles is a crucial step in LPA. Each profile represents a subgroup of individuals who share similar patterns of responses on a set of variables, which can provide insights into the underlying mechanisms driving their behaviour. Furthermore, the identification of the optimal number of profiles to represent a population is a critical issue in LPA. This involves balancing the complexity of the model with its ability to capture meaningful variability in the data, and requires careful consideration of both statistical and substantive criteria.


LPA has several advantages over traditional variable-centred approaches. It allows for a more nuanced understanding of the complexity of human behaviour, particularly in cases where individuals exhibit multiple and diverse patterns of behaviour across different sets of variables. 


In the context of information search behaviour, LPA can help to identify distinct groups of individuals who engage in different search strategies or have different search motivations. This can be useful for understanding how people search for information online, what factors influence their search behaviour, and how search behaviour relates to other variables such as task performance, satisfaction, and learning outcomes.


The purpose of this study was to investigate the relationship between individual differences in motivation, metacognition, and self-regulation and search behaviour. 
To classify participants into high and low groups based on their scores on these questionnaires, we employed LPA. 
LPA is particularly useful when the relationship between variables is not well understood or when it is difficult to determine which variables should be used to classify individuals into groups.
We employed LPA to identify latent profiles of participants based on their scores on the IMI, MAI, and SRQ questionnaires.
LPA is particularly useful when the relationship between variables is not well understood, or when it is difficult to determine which variables should be used to classify individuals into groups.




<!-- We employed Latent Profile Analysis (LPA) to identify groups (latent profiles) of participants based on their scores on the Intrinsic Motivation Inventory (IMI), Metacognitive Awareness Inventory (MAI), Self-regulation questionnaire (SRQ), and Memory Span (MS) task. -->


The results of the LPA showed that there were two distinct groups (latent profiles) of participants based on their scores on the IMI, MAI, SRQ, and MS: a high group and a low group (Figure \@ref(fig:lpa-profile-means)). The high group had generally higher average scores on the IMI, MAI, SRQ, and MS compared to the low group, indicating that they were more intrinsically motivated, more aware of their metacognitive processes, and had higher levels of self-regulation.


<!----------- fig:lpa-profile-transitions ----------->
```{r lpa-profile-transitions, fig.scap='(ref:scap-lpa-profile-transitions)', fig.cap = '(ref:cap-lpa-profile-transitions)',  echo=FALSE, out.width='100%', fig.align='center'}
nbShowFig("figs/lpa-profile-transitions")
```
<!-- each text reference needs to be their own single paragraph ! -->
(ref:cap-lpa-profile-transitions) Diagram illustrating, at different timepoints, how participants stayed within their same high/low LPA profiles (green) or changed profiles (orange). Grey trajectories indicate participants who dropped off and did not complete the study.

(ref:scap-lpa-profile-transitions) LPA Profile Transitions.

<!---- fig:lpa-profile-transitions (leave a blank line before this) ------>


Figure \@ref(fig:lpa-profile-transitions) illustrates the memberships in the two groups at different points in time, and how one participant (`P016_AUSTIN`) changed group membership at the end of the semester.
12 participants started off the semester (`QSNR1`) in the high group, while 4 in the low group.
The group membership remained the same in the middle of the semester (`QSNR2`).
At semester end, 4 participants from the high group and 2 participant from the low group dropped off.
One participant transitioned from high group to low group.
This resulted in 7 participants in the high group and 3 participant in the low group, with no data for 6 participants at the semester end timepoint (`QSNR3`)



Henceforth, in the discussion, all the **Effect Sizes (ES)** reported as part of Mann Whitney U test compare the scores of the low group (first distribution) with those of the high group (second distribution).
In other words, an example effect size $ES=0.19$ means that there is a 19% chance that a score from the low group will be greater than the corresponding score from the high group.





<!-- 

Latent Profile Analysis (LPA) is a statistical technique used to identify unobserved or latent subgroups within a population based on their responses to a set of observed variables.  

LPA is a powerful and flexible tool that can be used to gain insights into complex and multidimensional data, such as information search behavior. 

@ambrose2010howa said that students' motivation, metacognition, and self-regulation determines, directs, and sustains what they do to learn.
We were interested to study the effect of these traits on students' search behaviour.
So we collected self-perceived reports of all 3 of them.
However, these constructs are not single binary variables that provide nice groupings automatically.
Instead they are multidimensional data, and are only observable indicators at best of the real hidden (latent) characteristic of an individual. 
In order to employ these multiple constructs to cluster participants into groups, we turned to psychology literature and latent class and latent profile methods. 

and utilized latent class and latent profile methods. These statistical techniques allow us to identify and describe subgroups within a population based on shared patterns of responses across multiple variables. By using these methods to analyze the self-perceived reports of motivation, metacognition, and self-regulation, we hope to gain a deeper understanding of how these traits relate to students' search behavior. Ultimately, this information could inform the design of interventions that are tailored to specific subgroups of students with distinct profiles of motivation, metacognition, and self-regulation. 

Latent Profile Analysis (LPA) is one of the many approaches clustered together under the umbrella term person-centred statistical approaches, that is being increasingly used in Organizational Psychology, and child development research. LPA provides a framework for describing population heterogeneity in terms of differences across individuals on a set of behaviors or characteristics, as opposed to describing the variability of a single variable. This distinction has been described as a person-centered approach, in contrast to more traditional variable-centered approaches such as multiple regression analysis. The underlying principle of person-centered approaches is that, rather than quantifying the role of particular variables in a study, a population is organized in terms of a finite number of mutually exclusive and exhaustive subgroups, each comprising similar individuals. In other words, each Latent Profile (LP) represents a subgroup of individuals characterized by a pattern of responses on a set of variables; LPA is used to identify and describe the optimal number of LPs to represent a population. 



TODO: describe the high and low groups appropriately.

TODO: Describe stats from `HI` and `LO` profiles, as in YSC Sec 5.1.

- how the following changed over time 
  - motivation, metacognition, self regulation
  - perceived learning, perceived search outcome
 

TODO: change in mean and sig diff over time / task type
  - longitudinal phase
  - all
  - repeated task
  - non-repeated task
  - 

 TODO: 
- For each section below on measures
  - how the measure was operationalized 
  - what is the value / trend
  - 1-2 lines
- For Disucssion later
  - Pool together the 1-2 lines

Proposal (`PHASE2A`)
Outline (`PHASE2B`)
Rough Draft (`PHASE2C`)
Final Paper (`PHASE2D`) 

-->




## Learning and Search Outcomes

<!----------- fig:rp2-learning-search-outcomes ----------->
```{r rp2-learning-search-outcomes, fig.scap='(ref:scap-rp2-learning-search-outcomes)', fig.cap = '(ref:cap-rp2-learning-search-outcomes)',  echo=FALSE, out.width='100%', fig.align='center'}
nbShowFig("figs/rp2-learning-search-outcomes")
```
<!-- each text reference needs to be their own single paragraph ! -->
(ref:cap-rp2-learning-search-outcomes) Self-reported learning and search outcomes (a, b), and instructor assigned grades for the high and low groups (c).

(ref:scap-rp2-learning-search-outcomes) Self-reported learning and search outcomes, and grades received in the longitudinal phase.

<!---- fig:rp2-learning-search-outcomes (leave a blank line before this) ------>

Figure \@ref(fig:rp2-learning-search-outcomes) shows the mean values of the self-reported (perceived) learning outcomes (a), self-reported search outcome (b), and instructor assigned grades (c) for the Ethical Dilemma research paper writing task over the semester.
The self-reported learning and search outcomes are inspired from work by @collins2016assessing.

We see that the high group had higher levels of perceived learning outcome and perceived search outcome compared to the low group, and these differences were statistically significant: $(U = 115.0, p = .0005, ES = 0.19)$ for the learning outcome, and $(U = 151.0, p = .005, ES = 0.25)$ for the search outcome. 
(The effect sizes indicate the probability that a value chosen at random from the low group's scores will be greater than a value chosen at random from the high group's scroes.)



The fact that the high group had statistically significant higher self-reported learning outcomes and self-reported search outcomes suggests that these students may have had a higher level of motivation, self-regulation, and better time management skills than the low group. 
This is because students who are motivated and self-regulated tend to be more efficient and effective in their information searching behaviours, which in turn may lead to better learning outcomes. 
Additionally, the high group may have been better at managing their time and resources, which would allow them to engage in more thorough and comprehensive information searching activities.



The instructor assigned grades for the high group also generally stayed higher than the low group (except for the Proposal stage). However, the differences were small.
This may indicate that the instructors' grading criteria may not have fully captured the impact of information searching behaviours on learning outcomes.
This is because the instructor's grading criteria may have been focused more on the content of the research paper, rather than the process of information searching. As a result, students who were more effective in their information searching behaviours may not have received a higher grade, even if their research paper was of higher quality.
Another possibility is that the grading process may have been liberal towards the students.



@collins2016assessing reported that "searchers' perceived learning outcomes closely matched their actual learning outcomes" and this was also indirectly correlated with their information search behaviours in terms of dwell time on documents.
Let us examine in the following sections how the findings from the LongSAL study compare and contrast with those reported by @collins2016assessing and others.



<!-- The high group had statistically significant higher self-reported learning outcomes and self-reported search outcomes, compared to the low group.
The instructor assigned grades that they received also showed similar trend, but there was no significant difference in the grades. 

 The fact that the high group had statistically significant higher self-reported learning outcomes and self-reported search outcomes suggests that these students may have been more motivated, self-regulated, and better at managing their time and resources than the low group. 

 The finding that the high group had statistically significant higher self-perceived learning outcomes and self-perceived search outcomes suggests  

 Additionally, the lack of a significant difference in the grades assigned by the instructor  


Correlation of SPL with Grades

- self-perceived learning (SPL)
- grades
- paired t-tests for SPL with obtained grade
- CONCLUSION: obtained grades are not good indicators of learning 
- 
- -->



## Q: Query Formulations


### Length and Count of Queries per Search Task

<!----------- fig:rp2-query-length-count ----------->
```{r rp2-query-length-count, fig.scap='(ref:scap-rp2-query-length-count)', fig.cap = '(ref:cap-rp2-query-length-count)',  echo=FALSE, out.width='100%', fig.align='center'}
nbShowFig("figs/rp2-query-length-count")
```
<!-- each text reference needs to be their own single paragraph ! -->
(ref:cap-rp2-query-length-count) Lengths and count of queries for each search task in the Longitudinal Phase.

(ref:scap-rp2-query-length-count) Query length and counts -- longitudinal phase.

<!---- fig:rp2-query-length-count (leave a blank line before this) ------>


**Query length** was operationalized as the number of terms (words separated by spaces) in the search query that participants submitted to the search engines or other information retrieval sites.
Query length can vary from a single word to several phrases or a full sentence.
Longer search queries may indicate a more specific or complex information need, while shorter search queries may be more general or broad in scope.
**Queries count** per search task refers to the number of separate queries or search attempts that a participant issued in order to complete a task. 
This measure may vary depending on the complexity of the information need, the user's level of expertise with the search system, and other factors. 
<!-- This metric is commonly used in information retrieval research to evaluate the effectiveness of search systems and user search behavior. -->



Figure \@ref(fig:rp2-query-length-count) (a) and (b) shows the differences in total and average query length of the high and low groups, while Figure \@ref(fig:rp2-query-length-count) (c) illustrates the number of queries issued, at different stages of writing the research paper. 
The low group demonstrated a zig-zag pattern in their **total query length**, and **query count**, over the duration of the semester, with a low start at proposal, followed by a peak at outline, a dip at rough draft, and again a peak at Final Paper.
The high group had a steady increase in total query length and query count, from proposal to outline to rough draft, and took a very gentle dip (or remained steady) at final paper stage.
Comparing the total query length and query count to the **average query length** (Figure \@ref(fig:rp2-query-length-count) (b)), we see that the high group maintained a steady 4-5 terms per query throughout the semester, whereas the low group had a jump to more than 10 terms per query in the rough draft stage.


The low group issued a small number of short queries in the proposal, then a higher number of short queries during the outline, followed by an even smaller number of very long queries during the rough draft, and then a very large number of short queries during the final paper phase.
On the other hand, the high group kept issuing an increasing number of similar-length (short) queries throughout the semester.


Combining these results we can posit that the low group demonstrated signs of struggling throughout the semester [@hassan2014struggling].
These students may have struggled to effectively search for information at the beginning of the semester, but then increased their search efforts as the deadlines approached. The fact that they issued a smaller number of very long queries during the rough draft phase may indicate that they were not able to effectively refine their search strategies to find more relevant and useful information.
In contrast, the high group's pattern of issuing an increasing number of similar-length (short) queries throughout the semester suggests that these students may have had a more consistent and effective search strategy. They may have been better able to refine their search strategies over time, which allowed them to find more relevant and useful information throughout the different stages of the research paper writing process.




<!--

The number of queries issued per task (Figure \@ref(fig:ResP8027181930754266114)) followed a similar pattern as the total query length (Figure \@ref(fig:ResN7152194718394476899)).
The low group issued a steadily increasing number of queries as they progressed through the semester, from the Proposal to the Final Paper phase, overtaking the high group at the Outline phase.
Additionally, as their average query length was quite low while writing the Final Paper, it appears they were issuing a large number of small queries, indicating signs of struggling or exploring.
In contrast, the high group decreased their query submissions after the Outline phase, signifying they may have already collected the information they need in the earlier parts of the semester. 

Both the groups had similar average query length during the proposal, outline, and final paper stages.
However, there was a big difference in average query length in the rough draft stage, with the low group issuing more than 10 terms per query on average, while the high group kept at 4 terms per query. 


 The average length of queries issued by the high and low groups was not large during the Proposal (`PHASE2A`), Outline (`PHASE2B`), and Final Paper (`PHASE2D`) (Figure \@ref(fig:rp2-query-length-count) (b)).

However, the difference in average query length between the two groups was almost significant during the Rough Draft stage (`PHASE2C`), with the low group issuing around 8 words per query, whereas the high group issuing about 4 words per query.  


high group was slightly higher than the low group during the Proposal , and then became much less during the o  


were always longer than those issued by the low group, except before the Outline (`PHASE2B`) and the Final Paper submission (`PHASE2D`) (Figure \@ref(fig:ResP2136245316506143308)). 
 
For all tasks,  the high group issued longer queries than the low group (Figure ResP4090733126835336320),  
  
  
The low group, with lower levels of motivation, metacognition, and self-regulation, were issuing queries which were often two terms (words) shorter on average, than the corresponding queries from the high group. 


increased monotonically over the semester during (Figure \@ref(fig:ResN7152194718394476899)), with the longest queries being issued by this group before the Final Paper submission phase (`PHASE2D`).
On the other hand, queries from the high group were the longest during the Outline phase (`PHASE2B`), and then it decreased in the subsequent phases.

This indicates that the high group, with higher levels of motivation, metacognition, and self-regulation, were planning ahead in the early parts of the semester to find their references. 
On the other hand, the low group, with lower levels of those traits, possibly demonstrated a tendency to procrastinate or delay their work until the final paper.
A quote from participant `P006_HANOI` illustrates this phenomenon:

> *"so far for this rough draft I haven't actually had to google anything since I downloaded everything into pdfs during the outline stage and haven't needed any new material so far."*
>
> `r nbQuoteAuthor("--- P006_HANOI")`
> 



LO group had highest total query length before final paper (ResN5894660104957913932)


HI group had highest average query length during rough draft (ResP6726131652814458688)

LO group was slacking and putting it off till last minute.

 
issued higher number of queries during the early part of the semester -- Proposal and Outline -- but then they issued lower number of queries during the later parts of the semester, w.r.t. the high group.  


The difference in the number of queries issued by the two groups approached statistical significance while writing the Rough Draft.  

were the highest before the Rough Draft (`PHASE2C`) . 

Like avg query length, LO group issued highest number of queries when writing final paper, while HI roup did that during outline.
Even, one participant commendted "I had downloaded all the papers I needed during..." 

-->








### Query Reformulation Types (QRTs)

<!----------- fig:rp2-qrt ----------->
```{r rp2-qrt, fig.scap='(ref:scap-rp2-qrt)', fig.cap = '(ref:cap-rp2-qrt)',  echo=FALSE, out.width='100%', fig.align='center'}
nbShowFig("figs/rp2-qrt")
```
<!-- each text reference needs to be their own single paragraph ! -->
(ref:cap-rp2-qrt) Number of different query reformulation types (QRTs) as per taxonomy proposed by @liu2010analysis.

(ref:scap-rp2-qrt) Query reformulation counts for longitudinal phase.

<!---- fig:rp2-qrt (leave a blank line before this) ------>



Query reformulation refers to the process of modifying or refining a search query in order to improve the relevance of search results and better match the user's information needs (Section \@ref(sec-bg-search-query)). 
Query reformulation typically occurs due to a searcher's improved understanding of how to better translate their information need into a search query.
Using the taxonomy proposed by @liu2010analysis (Figure \@ref(fig:res-Q-QRT-txnmy)), we classified each previous-next query pair issued by participants into one of the five query reformulation types (QRTs):
New,
Generalization,
Specialization,
Word Substitution,
and 
Repeat.



We faced a challenge in disentangling **Repeat** queries from "hub-and-spoke" behaviour, where the user goes back and forth between a SERP and different content page by using the browser's forward and back buttons ^[The SERP is the hub, which represents the initial point of inquiry, while the spokes represent the subsequent branches of exploration along different content pages. This search behaviour is often used when users have a general idea of the topic they are interested in, but need to explore different facets of the topic to narrow down their search and find relevant information.].
Each back button press on the browser (to go back to the SERP from a content page) meant a fresh HTTP GET request was sent to the search engine. 
This resulted in YASBIL logging the move as a resubmission of the query.
So for the discussions that follows, **"Repeat" refers to repeat queries combined with hub-and-spoke behaviour.**.




The counts of the five QRTs are presented in Figures \@ref(fig:rp2-qrt) (a) through (e).
For the low group, the trend of counts followed similarly from their trends of query counts and total query lengths (Figures \@ref(fig:rp2-query-length-count) (a) and (c)), with varying intensities: alternating between high and low values at successive points in the semester.
For the high group, except Query Generalizations -- which followed a zig-zag pattern -- all the other QRTs showed an overall increase in count throughout the semester.

The high group issued the most number of new queries and generalized queries while writing the rough draft, whereas they had the highest number of specializations and word substitutions while writing the final paper.
The low group, on the other hand, had their lowest number of all types of QRTs, except repeat, while writing the rough draft.
The most interesting is the trend of Query Generalizations (Figure \@ref(fig:rp2-qrt)(b)), where the high group and low group demonstrated diametrically opposite behaviour: maxima at outline and final paper for the low group, whereas minima at those stages for the high group.
The high group also had significantly less number of repeat queries (or hub and spoke behaviour) throughout the semester, compared to the low group $(U = 228.0, p = .02, ES = 0.74)$.



The low group's fewer counts of all QRTs while writing the rough draft suggests that they may have struggled to effectively reformulate their queries throughout the different stages of the research paper writing process, perhaps due to the complexity and depth of the research required for the tasks.
The low group may have had more difficulty refining and targeting their search queries, resulting in more new and repeated queries at the final stage of the paper writing process. 
They may also have had more difficulty with the conceptualization of their research question or topic, leading to more generalizations and fewer specializations in their queries. 
Additionally, their higher number of repeat queries (or hub and spoke behaviour) may indicate that they were relying on a limited set of sources or search terms, which may have limited their ability to find new and relevant information.



The high group, however, had a different pattern of query reformulation compared to the low group. 
They had their highest counts of new queries and query generalizations in the Rough Draft Phase, and most specialization, word substitutions, and repeat queries while writing the Final Paper.
This indicates that their queries were more exploratory in the early part of the semester, and became more precise and refined in the later parts of the semester.
They may have been more proactive in identifying new avenues for research earlier in the semester. 
The highest count of query generalizations during the writing of the rough draft may suggest that they were better able to synthesize and generalize information from their sources at an earlier stage in the writing process. 
The high group may also have been better able to refine their search queries through word substitutions, which peaked while writing the final paper, indicating a greater level of precision and focus in their information seeking behaviour.
In contrast, the low group had their highest count of repeat queries during the outline and final paper, indicating that they may have had more difficulty finding and retaining relevant information throughout the research process.



We posit that the high group may have been more effective in their query reformulation strategies. 
Specifically, the high group may have been better able to identify new information needs as they worked on the rough draft, and then refine and specialize their queries as they worked on the final paper. 
This ability to adapt and refine their queries may have allowed them to find more relevant and useful information, which in turn may have contributed to their higher self-perceived learning and search outcomes.









<!--



followed a similarly from their trend of query lengths and query counts
The low group, in general issued more New queries, Generalizations, and Repeat queries (combined with hub-and-spoke moves) than the high group. 
On the other hand, the high group had more specializations and word substitutions in their queries than the low group.
The differences in Generalizations $(U = 218.0, p = .07, ES = 0.67)$
and Repeat queries $(U = 233.0, p = .05, ES = 0.69)$
were approaching statistical significance.
The trend in these reformulation counts across the semester are illustrated in Figures 

- ResP4758332161906858406 New
- ResP4519777880393782433 Generalization
- ResP8890916105505948535 Specialization
- ResP3490778183579127133 Word Substitution
- ResP6961499846675834400 Repeat


The low group had their highest counts of most query reformulation types while writing the final paper.
 For the low group, all the highest counts of new queries, query generalizations, query specializations, and repeat queries occurred during the writing of the final paper.  


Keeping this in mind, we observed that the low group issued a significantly higher number of repeat queries (or hub-and-spoke moves), compared to the high group $(U = 51.5, n_{low}=7, n_{high}=8, p=.0077, CLES=0.92)$.
The highest differences occurred in the Outline phase and the Final paper phase (Figure ResP7955607431899741484), with the low group issuing double the number of repeat queries $(6.11 \pm 3.7)$ on average, w.r.t. the high group $(3.51 \pm 2.8)$  

 When a user submits a search query that does not return satisfactory results, they may attempt to reformulate their query by using different keywords, rephrasing their question, or adding or removing search terms. Query reformulation can be done manually by the user or automatically by the search system using techniques such as query expansion or query suggestion. The goal of query reformulation is to help users find the information they are looking for more efficiently and effectively. 

The low group issued more number of New Queries (sig diff), more query generalizations, more query specializations, and more repeat queries (sig diff), compared to the low group. The high group had had more word substitutions in their queries.  

 also had their highest level of word subsitutions during the final paper writing phase. 
 
  The high group also showed a higher tendency towards query generalization and query specialization during the rough draft phase, while  

 the high group tending to have more word substitutions and fewer repeat queries compared to the low group.  

The high group also showed a higher tendency towards query generalization and query specialization during the rough draft phase, while the low group had higher counts of all query reformulation types during the final paper phase. 


Here are when the different query reformulation counts reached their maximum values during the semester, for the low and high groups:

Max values of query reformulation count for Low group:

- new queries: final paper
- query generalization: final paper
- query specialization: final paper
- word substitution: outline
- repeat queries: outline and final paper

Max values of query reformulation count for High group:

- new queries: outline and final paper
- query generalization: writing rough draft (after outline, before final paper)
- query specialization: outline
- word substitution: final paper
- repeat queries: rough draft 



 The low group issued more number of **New** queries in total (Figure ResN3873804091287075248) and on average (Figure ResP3026382842695489517), compared to the high group. 
During the Rough Draft and Final Paper phases, the low group exhibited heightened tendency to generate New search queries in their pursuit of novel information. 
On average, participants in the low group issued four more search queries than those in the HI group in these last two phases of the research project (Figure ResP3026382842695489517). 
This suggests that the LO group engaged in more active and extensive information-seeking behaviour, potentially reflecting a greater sense of urgency and pressure to complete their assignments.
The difference in total number of New queries between the groups approached significance $(U = 50.0, n_{low}=8, n_{high}=8, p=.06, CLES=0.78)$, with a moderately strong effect size. 



ResN8316003849035045794 
no. of new queries was the highest during final paper for the LO group
they were frantically searching for new information
on an average, each participant in the LO group was making 4 more search queries than those in the HI group during the final paper phase. 



The low group demonstrated a significantly higher count of total **Query Generalizations** $(U = 44.5, n_{low}=7, n_{high}=7, p=.01, CLES=0.91)$. 
While the high group issued a total of $2.57 \pm 2.1$ query generalizations per task the low group were issuing $9.86 \pm 6.7$ generalized queries for the same, across the entire study (Figure ResN3302769723271690264).
Query generalization is an indicative of exploratory behaviour, and this increase by the low group indicates a lack of specificity in the participants' information needs, which may lead to lower precision in search results. 

 The high group issued an average at least one word substitution for each search task.
The trend in the count of total **Query Specializations** was similar to that of Query Generalizations (Figure ResN6450294753032251158). 
The high group demonstrated the maximum number of query specialization before the Outline phase, whereas the low group did the same before the Final Paper phase.
While the difference was not significant, the effect size was moderately high $(U = 42.5, n_{low}=8, n_{high}=7, p=.10, CLES=0.76)$. 


**Word Substitutions** were performed in all the tasks by the high group, whereas the low group skipped it during Proposal, and the `PHASE3-BIAS` task (Figure ResN3108315939720148502).  
 

ResN3604624796642370520 generalizations
ResP5443351906342031714 specializations
ResN4290201084087196149 word substitutions
ResN9056495301645634830 repeat
Repeat must be taken with a grain of salt as repeat behaviour was diffcult to tease out from hub and spoke behaviour, if the user pressed the back button of the browser 

-->







### Entropy of Query Reformulation Types {#sec-res-phase2-query-H}

<!----------- fig:rp2-qrt-entropy ----------->
```{r rp2-qrt-entropy, fig.scap='(ref:scap-rp2-qrt-entropy)', fig.cap = '(ref:cap-rp2-qrt-entropy)',  echo=FALSE, out.width='100%', fig.align='center'}
nbShowFig("figs/rp2-qrt-entropy")
```
<!-- each text reference needs to be their own single paragraph ! -->
(ref:cap-rp2-qrt-entropy) Stationary and transition entropies of query reformulation type (QRT) sequences.

(ref:scap-rp2-qrt-entropy) Entropy of Query Reformulation Types for the Longitudinal Phase.

<!---- fig:rp2-qrt-entropy (leave a blank line before this) ------>

Entropy is a measure of the diversity or unpredictability of a sequence of events. In the context of search queries, entropy can be used to quantify the variability or randomness of the query reformulations issued by participants.
Transition analysis and entropy helps to cover differences in disparate tasks and activities.
Inspired by previous works in analysing eye-movement sequences [@krejtz2014entropy; @krejtz2015gaze] and search tactics sequences [@he2016beyond], we employed a similar entropy analysis of query reformulation sequences, and search tactic patterns of the participants.


For query reformulations, the possible set of states were the five query reformulation types:
Generalization, Specialization, Word Substitution, Repeat, and New.
If we consider a sequence of query reformulations issued by a participant 
(e.g., *New -> New -> Specialization -> Specialization -> Word Substitution -> Generalization*)
then this sequence can be considered as a first order Markov chain, wherein, the next step in the chain depends only on the current state.
Entropy analysis on these Markov chains quantifies how predictable the states are, and yields two categories of uncertainty measures: transition entropy, $H_t$, and stationary entropy $H_s$.
Similar stationary and transition entropy measures can be obtained for sequences of search tactics.



Guided by the above, we carried out entropy analysis of query reformulation sequences produced by the participants.
In the context of query reformulations, the maximum **transition entropy**, $s \log s$, can be reached when there is an equal probability of switching between each of the $s = 5$ states, or QRTs (query reformulation types). 
The minimum transition entropy (0) is achieved in a fully deterministic Markov chain, where all transition probabilities are either 1 or 0. 
This means that with a higher transition entropy there is more randomness in the participant's transitions between different QRTs. 
This randomness is an indication that the participants do not have a clear progression from one QRT to another. 
On the other hand, a lower transition entropy indicates that the participant's transition between QRTs are highly predictable.
**Stationary entropy** is calculated from the distribution of QRTs. 
A higher stationary entropy value indicates that the QRTs were used uniformly, while a lower stationary entropy indicates that some QRTs are preferred over others. 
Values of stationary entropy vary between 0 and $\log s$, where $s$ is the number of possible states (QRTs)^[This explanation is adapted from @he2016beyond].
All the entropy values presented in this chapter were normalized by their theoretical maximums, for equivalent comparison across different tasks.



The transition entropy of query reformulations followed interesting patterns for the low and high groups (Figure \@ref(fig:rp2-qrt-entropy)(a)). 
The low group had a V-shaped pattern showing a decrease in transition entropy from proposal to outline, then an increase from outline to rough draft to final paper. 
On the other hand, the high group had a zig-zag pattern, with low transition entropy during the proposal, an increase during the outline, a decrease during the rough draft, and then another increase during the final paper. 
This indicates that the low group had the least randomness in query reformulation strategies during the outline, while the high group had the most randomness at this stage. 
Subsequently, the randomness in the high group decreased, whereas that in low group increased.
This suggests that during the outline stage, the low group had a more structured approach to query reformulations, compared to the high group. 
However, as the semester progressed, the low group's approach became more random, while the high group's approach became structured. 
These pattern suggests that the low group may have struggled to adapt their query reformulation strategies as they moved through the different stages of writing the paper, while the high group was more able to adjust their strategies and maintain a predictable structure in their approach.




The stationary entropy of query reformulations of the low and high groups varied over the different phases of the research paper writing process as well (Figure \@ref(fig:rp2-qrt-entropy)(b)). 
The low group's stationary entropy reached its maximum value at the outline phase, whereas that for the high group became maximum at the rough draft phase.
This indicates that these two groups had distinct information searching behaviours throughout the writing process.
The low group tried out all possible types of query reformulations during the outline (as we saw from the query reformulation counts), and then settled on using repeat queries (or hub and spoke behaviour) more, during the rough draft phase. 
This lowered their stationary entropy at the rough draft phase, and may have limited their ability to find new and relevant information during the later stages of the writing process.


In contrast, the high group employed all the types query reformulations with equal probability during rough draft phase (Figure \@ref(rp2-qrt)), resulting in a higher stationary entropy value.
The increase in the high group's stationary entropy from outline to rough suggests that they were exploring a broader range of topics and concepts at this stage of the writing process, which may have allowed them to identify more relevant and useful information.
The subsequent decrease in stationary entropy from rough draft to final paper suggests that they were able to narrow down their focus and consolidate their understanding of the subject-matter as they progressed, which may have contributed to their higher self-perceived learning and search outcomes.



<!-- 
TODO SUMMARY: Overall, these findings suggest that there may be benefits to adopting a more exploratory and adaptive approach to information searching during the early stages of the research paper writing process, followed by a more focused and targeted approach as the writing process progresses. Future research could explore the specific strategies and techniques that are most effective in promoting this kind of adaptive and effective information searching behaviour among undergraduate students. 




The low group's approach varied more depending on the stage of the writing process, and thus they employed all the different types query reformulations uniformly (i.e. with equal probabilities). 
The 

was trying out all the query reformulation types as the semester progressed, whereas the

maintained a more consistent approach to their information searching behaviour, and thus preferred some query reformulation types more over others.
The high group's 




We computed the transition and stationary entropies of query reformulation types for  
 the entire task duration, as well as for the beginning one-third, middle one-third, and end one-third of each task duration for each participant. 
 
The results are discussed in the following sections. 
  
A higher query reformulation entropy indicates a greater degree of uncertainty or randomness in the user's query reformulation behaviour, indicating that the user may be struggling to find relevant information or is uncertain about their information needs. In contrast, a lower query reformulation entropy suggests a more systematic and directed approach to search, indicating that the user has a clearer understanding of their information needs and is using query reformulation strategies to efficiently retrieve relevant information. Query reformulation entropy is a useful metric for evaluating the effectiveness of search systems and understanding user search behaviour.

Transition entropy is a metric that measures the uncertainty or randomness in the transitions between different search states, such as between queries, documents, or web pages. It quantifies the level of unpredictability or randomness in the user's navigation behavior as they move from one state to another, and can be used to evaluate the efficiency and effectiveness of search systems and interfaces.

Stationary entropy, on the other hand, measures the uncertainty or randomness in the distribution of user behavior within a single search state. For example, it can be used to analyze the frequency and distribution of query terms used by a user during a search session, or the distribution of clicks on search results pages. Stationary entropy provides insights into the structure and characteristics of user search behavior within a given context, and can be used to optimize search algorithms and ranking models. 
 

the low group had the least randomness during outline, while the high group had the most during this stage. 
subsequently, the chaos in high group decreased, whereas that in low group increased


The high group may have had more efficient search strategies during the proposal and rough draft phases, but faced greater challenges during the outline and final paper phases, leading to more diverse query reformulation behaviours.  

The low group, however, may have had more consistent query reformulation behaviours throughout the different phases of the task, indicating less variability in their approach. 

differences were not significant over the entire duration of the tasks, there was a significant difference in the middle one-third interval of each task $(U = 131.0, p = .01, ES = 0.28)$.

-->


## URL Categorization for Analyzing Interactions

In order to understand the relationship between users' information search behavior and the type of webpages they visit, we needed to categorize webpages into different types. To accomplish this, we developed a classification system based on URL patterns.

URL patterns were first extracted from the web browsing data collected in our study. These URL patterns contain information about the structure and content of each webpage visited by the users. Based on this information, we were able to classify each URL present in the log data into the following hierarchical taxonomy:

- **`L`**: Search Result Pages, i.e., a **L**ist of Information Objects
  - **`L.PUB`**: Publication Search Results, e.g., on university library websites, digital libraries, Google Scholar, etc.
  - **`L.WEB`**: Web Search Engine Result Pages (SERPs)
- **`I`**: Content pages, i.e., Individual **I**nformation Objects
  - **`I.PUB`**: Academic Publications
  - **`I.WEB`**: Webpages that have the potential to provide relevant (academic) information for the search task, but are not publication. E.g., Wikipedia articles, relevant blog posts, government and non-profit websites, etc. Some of them were classified automatically (e.g., Wikipedia), while others were classified after manual inspection.
- **`MISC`**: URLs for webpages that did not fit in any of the above category

<!-- several different types, including search engine result pages, content pages, scientific peer-reviewed publications, Wikipedia articles, library websites, or other types of webpages. -->

To identify search engine result pages, we looked for URLs that contained URL query parameters such as `q` (Google, Bing), `search`, `query`, or `k` (Yahoo) along with specific strings associated with popular search engines such as Google or Bing. 
We also identified content pages by looking for URLs that contained strings such as "`article`", "`blog`", or "`news`".
Scientific peer-reviewed publications were identified based on URLs that contained specific strings associated with academic publishers or databases (ACM DL, Elsevier, Scopus, Springer etc.), while Wikipedia articles were identified by their URLs containing the string "`wikipedia`" in the hostname.
Library websites were identified by URLs that contained terms such as "library", "catalogue", or "database" as well as specific strings associated with major library systems (e.g., UT Austin uses Primo VE system from Ex Libris). Finally, we used the catch-all category `MISC` to identify other types of webpages that did not fit into any of the other categories.


The URL-based classification system provided a useful way to categorize webpages based on their type, allowing us to gain insights into how users' search behaviour varies across different types of webpages. By analysing the patterns of webpage types visited by users during their information search process, we were able to identify which types of webpages were most commonly visited and how they related to users' search behaviour.


<!-- 

TODO SUMMARY: Overall, the URL-based classification system provided a useful way to categorize webpages based on their type, allowing us to gain insights into how users' search behaviour varies across different types of webpages. By analysing the patterns of webpage types visited by users during their information search process, we were able to identify which types of webpages were most commonly visited and how they related to users' search behaviour. This information can be used to improve the design of information systems and search engines, as well as to inform the development of tailored interventions that support users' information search needs.
 -->



<!-- 

- peer-reviewed publications are `PUB`s
- others are `ARTICLE`s (e.g. Wikipedia)
- if no other info, then `WEB`
- fuzzy between `WEB` and `ARTICLE` (when classified manually)
- `ARTICLE` if there is a clear author
  - except `WIKIPEDIA`, due to common parlance
  - encyclopedias
- journal homepages are `WEB`
- list of chapters in a book are `L.PUB`.
  - e.g. in detail view of
- book chapter is `PUB`



 -->



## L: Interaction with Lists / Search Results -- Source Selection



### Number of Clicks per Query

<!----------- fig:rp2-query-click ----------->
```{r rp2-query-click, fig.scap='(ref:scap-rp2-query-click)', fig.cap = '(ref:cap-rp2-query-click)',  echo=FALSE, out.width='100%', fig.align='center'}
nbShowFig("figs/rp2-query-click")
```
<!-- each text reference needs to be their own single paragraph ! -->
(ref:cap-rp2-query-click) Number of clicks per query - longitudinal phase.

(ref:scap-rp2-query-click) Number of clicks per query - longitudinal phase.

<!---- fig:rp2-query-click (leave a blank line before this) ------>


Number of clicks per query refers to the number of times a participant clicked a link on a search result page after conducting a search query.
This metric reflects the level of interaction and engagement of the participant with the search results, as well as their ability to assess the relevance and usefulness of each search result presented to them.
<!-- This measure provides an indication of how much a participant engaged with the search results and how many different sources of information they explored while searching for relevant information.  -->
A higher number of clicks per query may indicate that the participant is more engaged and willing to explore a wider range of information sources, while a lower number may suggest a more focused and targeted search approach.
Figure \@ref(fig:rp2-query-click) shows the trend in total, average, and variability of clicks per query for the low and high groups at different points in the semester.




The low group had much higher total (Figure \@ref(fig:rp2-query-click)(a)) and average (Figure \@ref(fig:rp2-query-click)(b)) number of clicks per query than the high group, at all stages of the semester -- proposal, outline, and rough draft -- except the last stage: writing the final paper.
The maximum total number of clicks per query was during the outline phase (about 100 clicks total), while the maximum average number of clicks was during the rough draft phase (about 12 clicks per query on average).
The high group maintained a relatively low number of clicks per query during the proposal, outline, and rough draft stages (less than 4 clicks per query), and had the peak value during the final paper, with about 7 clicks per query.
Additionally, the high group had lower variability (standard deviation) in the number of clicks per query compared to the low group (Figure \@ref(fig:rp2-query-click)(c)).




The low group's higher total, average, and standard deviation of clicks per query throughout most of the semester, except for the final paper stage, suggests that they may have been less efficient in their searching behaviours, requiring more clicks and potentially spending more time on each query. 
The may have struggled to refine their search strategies, resulting in a higher number of clicks per query throughout the semester.
This could have contributed to their lower self-perceived learning and search outcomes.


In contrast, the high group's lower number of clicks per query throughout most of the semester, except for the final paper stage, suggests that they may have been more efficient and effective in their searching behaviours, requiring fewer clicks and potentially finding more relevant information per query. 
They may have been able to refine their search strategies and be more efficient during the semester, resulting in fewer clicks per query. 
This indicates the high group's ability to better assess the relevance and usefulness of search results, and to use their knowledge and cognitive strategies more effectively during the search process.
This could have contributed to their higher self-perceived learning and search outcomes.
The peak value of clicks per query for the high group during the final paper stage suggests that they may have needed to invest more effort in finding the most relevant and useful information for their final paper. 
However, even at this stage, their average number of clicks per query was still lower than the low group's peak value during the rough draft stage.


It is also possible that the differences in average clicks per query between the two groups during different phases of the semester reflect differences in the complexity or specificity of the information needed for the different tasks. For example, the paper outline phase may have required more broad and exploratory searches, while the final paper phase may have required more targeted and specific searches.






<!-- 
TODO SUMMARY Overall, these findings suggest that adopting more efficient and effective information searching behaviors and strategies, such as using more targeted queries and refining search terms, may be beneficial for improving self-perceived learning and search outcomes among undergraduate students. 
-->







<!-- 

The high group had fewer total clicks per query , and a lower average number of clicks per query , compared to the low group, across most of the tasks during the semester.
The low group had the highest average number of clicks per query when writing the rough draft (approx 12 clicks per query), while the high group had the highest average number of clicks per query while writing the final paper (approx 7 clicks per query).

This suggests that the high group was able to achieve better search outcomes with fewer clicks, indicating a higher level of efficiency in their search strategies.  
 
The high group having higher motivation, metacognition and self-regulation had lesser number of clicks per query in total, and on average, compared to the low group, over almost all the tasks during the semester. 
The variability (standard deviation) of the number of clicks per query of the high group was also less than the low group. All the differences were statistically significant.


ResP878771263343515297
HI group was more efficient. Average number of clicks per query was lower (less than 4) as they moved forward in the semester, with highest in the Outline phase.


ResN2805268620307804410

$(U = 1069.5, n_{HI}=56, n_{LO}=30, p=.03)$


ResN5118140679486679749
SD also says something 

-->







### Counts and Dwell Time on Search Results {#sec-phase2-res-L-dt}

<!----------- fig:rp2-l ----------->
```{r rp2-l, fig.scap='(ref:scap-rp2-l)', fig.cap = '(ref:cap-rp2-l)',  echo=FALSE, out.width='100%', fig.align='center'}
nbShowFig("figs/rp2-l")
```
<!-- each text reference needs to be their own single paragraph ! -->
(ref:cap-rp2-l) Interactions with search results - Longitudinal Phase.

(ref:scap-rp2-l) Interactions with search results - Longitudinal Phase.

<!---- fig:rp2-l (leave a blank line before this) ------>





The Ethical Dilemma research paper writing task involved searching for 20 references, and incorporating them into the narrative of the research paper.
Therefore, we structure the discussion around visits to scholarly publication search results, and (non-scholarly) web SERPs.
Examples of scholarly publication websites are Google Scholar, digital libraries such as ACM DL, Springer, Elsevier, PubMed and others.
We examined how visits to these two categories of websites changed across the different stages of writing the research paper for each group. 
Figure \@ref(fig:rp2-l) shows the counts of publication search results and web search results visited by the two groups, as well as total and average dwell time on such pages by both the groups.



<!-- 

Low group had greater average dwell time on academic publication search results in all the four stages, viz. proposal, outline, rough draft, and final paper, compared to the high group.
Total dwell time of the low group was also higher, except at the final paper stage, when the high group surpassed the low group in dwelling on search results.

--->

For both publication search results and web search results, the high group visited a more number of those webpages than the low group (Figure \@ref(fig:rp2-l)(a) and (b)).
The high group visited more publication search results during the outline phase, and more web SERPs during the rough draft phase.
The low group on the other hand, had a dip in their visit count for both the search result categories during the rough draft phase.
However, they had significantly longer average dwell time on academic publication search results, in all the four stages, compared to the high group $(U = 153.0, p = .01, ES = 0.77)$ (Figure \@ref(fig:rp2-l)(e)).
Total dwell time of the low group was also longer, except at the final paper stage, when the high group surpassed the low group in dwelling on publication search results. 
The difference was approaching significance $(U = 138.0, p = .08, ES = 0.70)$ (Figure \@ref(fig:rp2-l)(c)).
<!-- indicating they were relying more on their collected results from earlier in the semester; and/or, their lower levels of motivation, metacognition, and self-regulation caused them to invest less effort in the search process at this point in the semester. -->
This suggests that the low group spent more time examining and considering scholarly publication search results compared to the high group. 
It is possible that the low group's lower levels of self-regulation and metacognition may have led them to spend more time on search results, as they may have found it harder to quickly evaluate and assess the relevance of search results to their task. 
On the other hand, the high group's higher levels those individual traits may have enabled them to quickly identify relevant search results and move on to the next stage of their task. 
However, at the final paper stage, the high group spent more time on search results as they may have needed to ensure that they had not missed any important information and had thoroughly covered their topic. 




In general, the high group engaged more with web search results, and less with scholarly publication search results.
The low group demonstrated the opposite pattern.
This is an interesting finding. 
<!-- It suggests that the high group may be more efficient in quickly finding and evaluating information on the web, while the low group may take longer to navigate and process the same information.  -->
The high group may have relied more on web search engines and popular sources, such as news articles or blogs, to get a broader understanding of their research topic and its context. 
In contrast, the low group may have relied more on scholarly publications to find more in-depth and specialized information.
They may have been more thorough in searching for and evaluating academic publications, which was arguably one of the main aspects of writing the research paper.
<!-- relied more on scholarly publication search engines.  -->
This difference in strategy may have contributed to the difference in perceived learning outcomes between the two groups. 
The high group may have been able to find a broader range of information from a variety of sources, while the low group may have limited themselves to more specialized sources. 
It is also possible that the high group's use of web search engines may have resulted in them encountering more diverse perspectives and interpretations of the research topic, which could have enhanced their critical thinking and analytical skills.


<!-- On the other hand, the low group may be more thorough in searching and evaluating academic publications (which was arguably one of the main aspects of writing the research paper), while the high group may be able to quickly identify and select relevant publications.  -->







<!-- TODO SUMMARY 

It is important to note, however, that the use of scholarly publications may not necessarily guarantee better quality information or higher self-perceived learning outcomes. 
The relevance and credibility of the sources used, as well as the ability to critically evaluate and synthesize the information, are important factors that can impact the effectiveness of the search and learning outcomes.

The quality of information is not solely determined by the type of source, but rather by the relevance, credibility, and reliability of the information found. 
While scholarly publications may provide more specialized and in-depth information, they may not always be the most relevant or up-to-date sources for a given research topic.
On the other hand, web search results may provide a broader range of sources, including news articles, blogs, and websites, that can offer alternative perspectives and insights on the research topic. 
However, the quality and reliability of the information found in these sources may vary, and it is important to critically evaluate and verify the information before using it in a research paper.

In addition, the ability to synthesize and integrate information from different sources, regardless of their type, is a key skill in conducting research and writing a research paper. 
This involves the ability to critically evaluate the relevance and credibility of the sources, as well as to identify and articulate the relationships between different pieces of information.

Overall, the choice of sources and the search strategies used should be based on the research question, the scope of the project, and the specific information needs of the researcher. Both scholarly publications and web search results can provide valuable information, and the key is to use them effectively and efficiently in order to achieve the desired learning outcomes. 

-->







<!--

high group had longer dwell times on web search results and shorter dwell time on publication search results. low group had the opposite pattern.

#### Web Search Results (SERPs) 


Low group had lower values of motivation, self regulation and metacognition. High group had high values of those.
Across all the stages, Total Dwell Time (seconds) on Web SERPs was higher for the high group, and lower for the low group.
Average Dwell Time (seconds) on SERPs was higher for the high group, and lower for the low group.
Dwell time for high group decreased from proposal to outline, then increased from outline to rough draft, and then decreased during final paper.
Dwell time for low group decreased from proposal to outline; minimum during rough draft, and then increased again during final paper.
 
 
For the high group, dwell time decreased from proposal to outline, then increased from outline to rough draft, and then decreased again during the final paper stage. This suggests that participants in the high group spent less time on SERPs during the outline stage but spent more time during the rough draft stage. However, they spent less time again during the final paper stage.
For the low group, dwell time decreased from proposal to outline and then reached a minimum during the rough draft stage. However, it increased again during the final paper stage. This suggests that participants in the low group spent the least amount of time on SERPs during the outline and rough draft stages but spent more time during the final paper stage.
This indicates at the positive relationship between individual differences in motivation, self-regulation, and metacognition and the amount of time spent on SERPs during a search task.

The high group's higher levels of motivation, self-regulation, and metacognition may have enabled them to engage in more effective and efficient search behaviours, leading to longer dwell times on Web SERPs. 
The higher dwell time on SERPs for the high group may indicate that they are more strategic and deliberate in their search behaviour, taking the time to carefully examine search results and evaluate their relevance to their information needs. This could be related to their higher levels of motivation, self-regulation, and metacognition, which enable them to set goals, monitor their progress, and adjust their strategies as needed to achieve optimal outcomes.

In contrast, the low group's lower levels of these individual differences may have hindered their ability to engage in effective search behaviours, leading to shorter dwell times on SERPs.
This suggests a more haphazard approach to search behaviour, with less attention to evaluating search results and less ability to regulate their search strategies. This may be related to their lower levels of motivation, self-regulation, and metacognition, which may limit their ability to set clear goals, monitor their progress, and make effective decisions in their search behaviour.


The high group was more efficient in their SERP examination, as they had lower total dwell times (Figure \@ref(fig:ResN7791839245731529625)) but higher average dwell times (ResP1938217350834571785) on SERPs compared to the low group. 
On the other hand, the low group had higher total dwell times, but a lower average dwell time on SERPs, which may indicate that they spent more time browsing through all the different SERPs, but spent less time on each individual SERP. 
The low group's dwell time pattern also showed a decrease in average dwell time during the outline stage, and stayed at the decreased value during rough draft stage, which could suggest that they struggled more with refining their search queries and examining search results during this stage.
The low group may have been more willing to spend time examining search results and exploring different options, while the high group may have been more efficient in quickly identifying and selecting relevant results.
The differences in total dwell time was significantly different in the beginning one-third $(U = 0.0, p = .02, ES = 0.00)$, middle one-third $(U = 16.0, p = .02, ES = 1.00)$, and end one-third $(U = 16.0, p = .02, ES = 1.00)$ portions of the tasks.  

-->











## I: Interaction with Information Objects -- Sources / Content Pages

<!----------- fig:rp2-i ----------->
```{r rp2-i, fig.scap='(ref:scap-rp2-i)', fig.cap = '(ref:cap-rp2-i)',  echo=FALSE, out.width='100%', fig.align='center'}
nbShowFig("figs/rp2-i")
```
<!-- each text reference needs to be their own single paragraph ! -->
(ref:cap-rp2-i) Interactions with content pages - Longitudinal Phase.

(ref:scap-rp2-i) Interactions with content pages - Longitudinal Phase.

<!---- fig:rp2-i (leave a blank line before this) ------>


We analysed interactions with content page in the same manner as counts and dwell time on search results (Section \@ref(sec-phase2-res-L-dt)): looking at visits to scholarly publications, vs visits to non-scholarly content pages.
Figure \@ref(fig:rp2-i) shows the counts of scholarly publications and non-scholarly content pages visited by the low and high groups, as well as total and average dwell time on such pages by both groups.


In a similar vein to publication vs web search results (Section \@ref(sec-phase2-res-L-dt)), the high group engaged less with scholarly publications, and more with non-scholarly content pages, compared to the low group.
Earlier in the semester, while writing the outline, the low group visited more academic publications, while the high group visited more content pages.
The trend reversed later in the semester while writing the final paper, when the low group viewed less number of publications and more content pages, while the high group did the opposite (Figures \@ref(fig:rp2-i)(a) and (b)).


Speaking of dwell times, the low group spent significantly more time viewing academic publications, in total $(U = 219.0, p = .04, ES = 0.71)$ and on average $(U = 227.0, p = .02, ES = 0.74)$, compared to the high group (Figures \@ref(fig:rp2-i)(c) and (e)).
While writing the rough draft, the high group spent more time viewing non-scholarly content pages.


The high group's preference for non-academic content pages may reflect their use of web search engines to find relevant information, as such search engines may often prioritize non-academic content over scholarly publications. 
The high group seemed to be more focused on finding information that was relevant to their topic, regardless of its source. They also appeared to be more interested in exploring a wider range of topics and concepts, which is reflected in their higher stationary entropy of query reformulations during the rough draft phase.



On the other hand, the low group's preference for academic publications may reflect their reliance on scholarly publication search engines to find information, as they may have perceived that being the main ask of the research paper. 
The low group seemed to be more concerned with finding information from scholarly publications, perhaps as a way to demonstrate the rigour of their research. 
They also appeared to have a more limited scope of inquiry, as reflected in their lower stationary entropy of query reformulations during the rough draft phase.



Overall, these findings suggest that the high group may have been more creative and adaptable in their information searching behaviours, while the low group may have been more rigid and focused on adhering to traditional academic norms.























<!-- 

The total and average dwell time of the high and low groups also showed some differences in their information behaviors. The low group had a higher total dwell time on academic publications compared to the high group, indicating that they spent more time engaging with scholarly sources. However, the average dwell time on academic publications was higher for the high group, suggesting that they engaged more deeply with these sources.

On the other hand, the high group had a higher total dwell time on non-academic content pages, while the low group had a higher average dwell time on these pages, indicating that the high group engaged more frequently with non-academic sources but the low group engaged more deeply with them.

Their total dwell time on such pages were also longer than the high group, but the average dwell time was shorter.
This suggests that the low group engaged in more exploratory behaviour, perhaps looking for additional sources of information or inspiration, beyond the academic publications. 
However, their lower average dwell time on these pages indicates that they may have been quickly scanning or skimming through the content, rather than engaging with it in depth. 
It's possible that they were spending less time on average on these pages because they were not as relevant or useful for their research paper. 

On the other hand, the high group may have been more focused on finding academic sources for their paper, which could explain their lower number of visits to non-academic content pages.
They may have been more focused on the task at hand and less likely to be distracted by extraneous information. 
The longer average dwell time on content pages suggests that they were more deeply engaging with the material they did visit. 
Overall, the low group may have been more inclined to explore a broader range of information sources, while the high group was more focused on academic sources and more likely to engage deeply with the content they did view.


Overall, these differences in the total and average dwell time suggest that the low group may have been more deliberate and selective in their engagement with scholarly sources, while the high group may have been more exploratory and open to a wider range of sources.



TODO SUMMARY: However, it's important to note that both types of sources can provide valuable information, and a balanced approach that considers a variety of sources may be most effective in conducting comprehensive research. 

This indicates that the low group had a more exploratory approach towards their research earlier in the semester, as they spent more time looking through a larger number of academic publications while writing the outline. On the other hand, the high group had a more focused approach, spending more time on fewer publications during the later stages when writing the rough draft and the final paper.
This may be an indication of a difference in information-seeking behaviour and strategies between the two groups, with the low group possibly using a more broad and inclusive approach to gather information, while the high group uses a more selective approach. It could also reflect differences in the stage of research and writing that the two groups were at during each stage, with the low group at a more exploratory stage earlier in the semester, while the high group was at a more advanced stage of writing.


The total and average dwell time (possibly reading time) also followed a similar pattern. 
The high group had longer dwell time on publications in total and on average, in the later parts of the semester, while the low group dwelt more on publications in the earlier parts of the semester.
This suggests that the high group had a more focused and deliberate approach to their research process, possibly due to better metacognitive and self-regulation skills. They spent more time on each publication, reading and analysing it thoroughly, in the later parts of the semester when they were working on the rough draft and final paper. This behaviour could have led to a deeper understanding of the content and better integration of the information into their writing. On the other hand, the low group may have had a more scattered approach, possibly due to lower levels of motivation, self-regulation, and metacognitive awareness, resulting in spending less time on each publication and viewing a larger number of publications earlier in the semester. 
This behaviour could have resulted in a superficial understanding of the content and difficulties in integrating the information into their writing. 

-->




<!-- ### Non-scholarly / Normal Content pages 
 

Count


Low group visited more number of content pages that were not academic publications compared to the high group.
Their total dwell time on such pages were high, but the average dwell time was low.


Dwell Time

the task that they were doing was to write a research paper at least twenty external sources

 -->







## Search Result Pages vs Content Pages

<!----------- fig:rp2-lvi ----------->
```{r rp2-lvi, fig.scap='(ref:scap-rp2-lvi)', fig.cap = '(ref:cap-rp2-lvi)',  echo=FALSE, out.width='100%', fig.align='center'}
nbShowFig("figs/rp2-lvi")
```
<!-- each text reference needs to be their own single paragraph ! -->
(ref:cap-rp2-lvi) Differences in interactions with search results vs. content pages.

(ref:scap-rp2-lvi) Differences in interactions with search results vs. content pages - longitudinal phase.

<!---- fig:rp2-lvi (leave a blank line before this) ------>


Figure \@ref(fig:rp2-lvi) describes differences in visits to all search results pages versus all content pages (scholarly and non-scholarly combined), for the high and low groups.
The high group visited more search result pages and content pages as the semester progressed, while the low group had a drop in these visits after the outline phase (Figure \@ref(fig:rp2-lvi) (a), (b)).
The difference in number of Search Results visits to Search Results pages was almost significant $(U = 136, p = .07, ES = 0.33)$.
This suggests that the high group may have been more engaged and persistent in their information searching behaviours, while the low group may have experienced a decrease in motivation or self-regulation as the semester progressed, specifically before writing the rough draft.
It is also noteworthy that the low group had a rebound in the number of pages visited while writing the final paper. This could indicate that they were able to re-engage with the task and their information searching behaviours improved as the final-paper deadline approached.



However, although the high group visited more number of all pages, they dwelt less on search results, and more on content pages. 
The differences are significant for total and average dwell times on search results (Figure \@ref(fig:rp2-lvi) (c) and (e)).
This indicates that the high group was more efficient at evaluating search result pages and quickly identifying relevant content. 
On the other hand, the low group may have spent more time on search result pages, possibly indicating that they had a harder time evaluating and selecting relevant results. 
This difference in information behaviour could be related to the higher self-perceived learning outcomes and search outcomes seen in the high group, as they were able to efficiently find and engage with relevant content.




<!-- 

The fact that the total dwell time on webpages followed a similar pattern as the number of pages visited is also interesting. It suggests that the high group spent more time engaging with the content they found, which could have contributed to their better learning outcomes. 

 High group visited more search result pages and more content pages as the semester progressed, while we see a drop for the same for the low group, especially after the outline phase, while writing rough draft.
Then there is again an increase in the number of pages visited by the low group while writing the final paper.
The total dwell time on webpages also follow a similar pattern. 

-->







## Entropy of Search Tactic Sequences

<!----------- fig:rp2-tactic-entropy ----------->
```{r rp2-tactic-entropy, fig.scap='(ref:scap-rp2-tactic-entropy)', fig.cap = '(ref:cap-rp2-tactic-entropy)',  echo=FALSE, out.width='100%', fig.align='center'}
nbShowFig("figs/rp2-tactic-entropy")
```
<!-- each text reference needs to be their own single paragraph ! -->
(ref:cap-rp2-tactic-entropy) Entropy of search tactic sequences for longitudinal phase.

(ref:scap-rp2-tactic-entropy) Entropy of search tactic sequences for longitudinal phase.

<!---- fig:rp2-tactic-entropy (leave a blank line before this) ------>


Similar to entropy analysis of Query Reformulation types (Section \@ref(sec-res-query-H)), we performed entropy analysis of search tactic transitions.
This analysis is directly inspired from @he2016beyond, who in turn were inspired from [@krejtz2014entropy, @krejtz2015gaze].
To characterize the entropy of students' search tactics, we used the following set of states, or tactics:

1. **`QUERY`**: issuing a search query
2. **`CLICK`**: mouse click
3. **`IDLE`**: participant stays idle for more than one minute (adapted from @taramigkou2018leveraging)
4. **`SESSION_BREAK`**: participant becomes idle for more than 30 minutes (Google Analytics defines a session break as 30 minutes of inactivity ^[https://support.google.com/analytics/answer/2731565#zippy=%2Cin-this-article])
5. **`L.PUB`**: visiting a publication search result page
6. **`L.WEB`**: visiting a web SERP
7. **`I.PUB`**: visiting a scholarly publication
8. **`I.WEB`**: visiting a non-scholarly content page
9. **`TASKPAGE`**: visiting webpages related to the study, i.e. the Qualtrics questionnaires

In the context of search tactic transitions, a higher value of transition entropy ($H_t$) indicates more randomness and uncertainty in the participant's search behaviour (which is composed of different search tactics, and transitioning or switching between those tactics).
A lower value of transition entropy indicates that the search behaviour (i.e. tactic switching behaviour) is highly predictable.
For stationary entropy of search tactics ($H_s$), a higher value indicates that participants utilize all the search tactics with equal probability, while a lower value suggests that certain search tactics are favoured over others.
Figure \@ref(fig:rp2-tactic-entropy) describes the trends in this values over the duration of the semester.
<!-- all search tactics are used uniformly, whereas a lower value indicates that some search tactics are more preferred over others. 
The entropies discussed in the following sections were normalized by their theoretical maximums, for equivalent comparison across different conditions. 
-->

The low group demonstrated a sharp increase in both transition entropy and stationary entropy of search tactics from the proposal stage to the outline stage.
Both the entropies subsequently decreased in the final paper stage.
The high group had a relatively stable trend in their transition entropy of search tactics, while their stationary entropy decreased as the semester progressed.
Also, the high group's stationary entropy was significantly lower than that of the low group $(U = 252.0, p = .04, ES = 0.70)$.

The low group's sharp increase in both transition and stationary entropy from the proposal to the outline stage suggests that they were exploring a wider range of search tactics and were less certain of which tactics to use during the early stages of the writing process. 
This is consistent with their high number of query reformulations and their tendency to click on a high number of search results and content pages.
The subsequent decrease in both entropies in the final paper stage suggests that the low group became more focused and efficient in their search tactics, possibly as a result of the feedback they received during the earlier stages of the writing process.


The high group's relatively stable trend in transition entropy suggests that they were consistent in their use of search tactics throughout the writing process. 
However, their decreasing stationary entropy suggests that they became more focused and efficient in their use of search tactics as the semester progressed, which is consistent with their lower number of query reformulations and their tendency to dwell more on content pages.


Overall, the differences in the entropies between the two groups suggest that the low group was more uncertain and exploratory in their search tactics, while the high group was more focused and efficient.







 




## Summary

We summarize the findings from this chapter, on the longitudinal searching-as-learning task of writing a research paper, as follows.


Participants were divided into high and low groups based on their self-reported values of motivation, metacognition, self-regulation, and memory span.
Their search behaviour and perceived learning and search outcomes were studied over the course of a semester.
During the longitudinal phase, both the high and low groups exhibited changes and differences in their search behaviour from the proposal to the outline stage to the rough draft, and finally to the final paper stage. 


Transition entropy refers to the uncertainty of the next search tactic that a user will apply during their search. 
In other words, it is a measure of how much the user explores different search tactics over the course of their search.
Stationary entropy refers to the uncertainty of the search tactic distribution over time. 
It is a measure of how stable or consistent the user is in their use of search tactics throughout their search process.
The low group showed sharp increases in both transition entropy and stationary entropy of search tactics from the proposal stage to the outline stage, followed by a decrease in both entropies in the final paper stage. 
This indicates that their search tactics became more diverse and unpredictable in the middle stages of the task, possibly due to uncertainty and lack of clarity on the topic.
The high group had a relatively stable trend, or gentle increase in their transition entropy of search tactics, indicating that they had a consistent and well-defined search strategy.
This group's stationary entropy decreased as the semester progressed, suggesting that they became more focused and efficient in their search tactics over time.
Additionally, the high group's stationary entropy was significantly lower than that of the low group, indicating that they had a more structured and organized approach to their search tactics.


Regarding learning and search outcomes, the high group demonstrated significantly higher perceived learning and search outcomes compared to the low group. 
Although the high group received slightly better grades on their research paper assignments, though there was no significant difference between the two groups. 
Possibly, other factors beyond self-perceived searching and learning outcomes may have contributed to the overall grade.






<!-- 

Both the low and high group had an increase in transition entropy and stationary entropy of search tactics from the proposal stage to the outline stage, followed by a subsequent decrease in both entropies in the final paper stage.

The high group had a relatively stable trend in their transition entropy of search tactics, while their stationary entropy decreased as the semester progressed. The high group's stationary entropy was significantly lower than that of the low group.

For the repeated task on personal finance, both the groups showed an increase in transition entropy of query reformulations from the beginning of the semester to the end, and an increase in transition entropy for the non-repeated tasks.

The high group reported higher learning and search outcomes for both repeated and non-repeated tasks, at both the beginning and the end of the semester. The low group's perceived learning and search outcomes decreased for all tasks at the end of the semester.

Both the high and low group showed a decrease in the number of clicks per query and the number of pages visited from the beginning to the end of the semester.
 -->


















<!-- 


ResN7289045485214067875 
Both groups had highest Ht during 2C (and also 3 Finance?)

ResP5638176378435107439 - beginning
ResN3435548740759333098 - middle
ResP6845508037293675246 - end

No sig diff for whole task, and at the beginning of task
Sig diff appeared at the middle and increased at the end of task (similar to as observed by Gwizdka).



ResP8685879301269737254
LO group had hghest Hs in 2C
No sig diff in overall task

No diff at beginning.
Diff is most prominent at middle (ResN1140102300744288543)
and also somewhat at end (ResN663758335140886910)




and high group increased as the semester progressed, from paper outline to 

Transition entropy remained lower for HI group at beginning, middle and end

For repeated task (finance) HI group stopped querying from the middle of the task.
Hi group felt more certain (TODO: get quote from response?)
While LO group continued till the end to query - they were more uncertain.

TODO: add network figure? 




ResN2968292861275564559 - whole
stationary entropy

Stationary entropy:
for HI goup
high in the beginning of task
then low at the end of task
their chaosness decreased as they progressed through the tasks, while for the LO group, their uncertainty increased?



ResN634943316862196398 - beginning
ResN6777243644016606483 - middle
ResN6573661794052961083 - end -->




<!-- ### Query Location

where did participants query?
Google, Library, etc 




R!esN7928923989685423424 is a VERY good result!
Model ID = 10




More plots are in Appendix \@ref(app-plots), such as Figure \@ref(fig:ResP5183239600404564866)




The results of your longitudinal study on information searching behaviors of undergraduate university students vis-a-vis their learning outcomes while writing a research paper can be presented in the following manner:

1. Overview of Participants: Begin by describing the participants in your study. Provide details about their demographic characteristics, academic majors, and other relevant background information.

2. Latent Profile Analysis: Describe the methodology used for the latent profile analysis and the resulting groups. Provide details on the composition of the high and low groups based on self-reported values on motivation, metacognition, and self-regulation.

3. Information Searching Behaviors: Present the results of the longitudinal tracking phase of the study, focusing on the information searching behaviors of the high and low groups. Compare and contrast the strategies used by the two groups, including the number and types of information sources consulted, the time spent on information seeking activities, and the perceived effectiveness of their information searching behaviors.

4. Learning Outcomes: Discuss the learning outcomes of the high and low groups, as measured by their research paper grades and their self-reported satisfaction with their research process. Analyze the relationship between information searching behaviors and learning outcomes, and identify any significant differences between the two groups.

5. Correlation Analysis: Conduct a correlation analysis between the participants' demographic characteristics and their information searching behaviors and learning outcomes. Analyze the findings and identify any significant correlations.

6. Final Phase: Present the results of the final phase of the study, which was conducted at the end of the semester. Discuss any changes in the information searching behaviors of the participants, and whether these changes were related to their learning outcomes.

7. Conclusion: Summarize the main findings of the study, highlighting the most important results and their implications. Discuss any limitations of the study and suggest directions for future research. 
-->


<!--

 --------------- context: ------------

For my PhD dissertation I conducted a longitudinal study of information searching beaviours of undergraduate university students vis a vis their learning outcomes while writing a research paper.
Participants were grouped into high and low groups using Latent Profile Analysis, from self-reported scores on motivation, metacognition, self-regulation, and memory span.
The task that they were doing was to write a research paper citing at least twenty external sources.
The writing involved four stages spread across the semester: proposal, outline, rough draft, and final paper.
Let us discuss some of the findings.

<result>
Why?

context: initial final:
apart from the longitudinal phase of the study, participants also completed two search tasks at the beginning of the semester, and two search tasks at the end of the semester.
One set of tasks, on the topic of "personal finance for college students", was repeated at the end of the semester.
The other set of tasks was not repeated. The topics were "ubuntu ethics" in the beginning of the semester, and "algorithmic bias" at the end of the semester.
Let us know discuss some of the findings for these tasks, and reason why the participants behaved in the ways they did, by drawing upon findings from the longitudinal phase as well.

--------------- context: ------------



Listed below are one line results for all the computed measures of my study.
Analyse them and help me write the results chapter of my dissertation.


Overall, the high group demonstrated higher levels of engagement with search results, with a higher total number and average number of clicks per query, and a higher variability of clicks per query. However, there were no significant differences between the groups in terms of the number, total length, average length, or variability of query length, or in terms of the transition entropy of query reformulations for the entire task. These findings suggest that engagement with search results may be an important factor in the success of undergraduate students in writing research papers.

Search Bheaviour Measures:









































-->