# Results: Repeated vs New Search Tasks



Same LPA profiles from Section \@ref(sec-res-lpa).



## Learning Outcomes

<!----------- fig:rp13-learning-search-outcomes ----------->
```{r rp13-learning-search-outcomes, fig.scap='(ref:scap-rp13-learning-search-outcomes)', fig.cap = '(ref:cap-rp13-learning-search-outcomes)',  echo=FALSE, out.width='100%', fig.align='center'}
nbShowFig("figs/rp13-learning-search-outcomes")
```
<!-- each text reference needs to be their own single paragraph ! -->
(ref:cap-rp13-learning-search-outcomes) Learning and Search Outcomes – Longitudinal Phase.

(ref:scap-rp13-learning-search-outcomes) Learning and Search Outcomes – Longitudinal Phase.

<!---- fig:rp13-learning-search-outcomes (leave a blank line before this) ------>







## Q: Query Formulations


### Length and Count of Queries per Search Task

<!----------- fig:rp13-query-length-count ----------->
```{r rp13-query-length-count, fig.scap='(ref:scap-rp13-query-length-count)', fig.cap = '(ref:cap-rp13-query-length-count)',  echo=FALSE, out.width='100%', fig.align='center'}
nbShowFig("figs/rp13-query-length-count")
```
<!-- each text reference needs to be their own single paragraph ! -->
(ref:cap-rp13-query-length-count) Query Lengths and Counts – Repeated vs Non-repeated Tasks.

(ref:scap-rp13-query-length-count) Query Lengths and Counts – Repeated vs Non-repeated Tasks.

<!---- fig:rp13-query-length-count (leave a blank line before this) ------>







### Query Reformulation Types (QRTs)

<!----------- fig:rp13-qrt ----------->
```{r rp13-qrt, fig.scap='(ref:scap-rp13-qrt)', fig.cap = '(ref:cap-rp13-qrt)',  echo=FALSE, out.width='100%', fig.align='center'}
nbShowFig("figs/rp13-qrt")
```
<!-- each text reference needs to be their own single paragraph ! -->
(ref:cap-rp13-qrt) Number of Query Reformulation Types (QRTs) – Repeated vs Non-repeated Tasks.

(ref:scap-rp13-qrt) Number of Query Reformulation Types (QRTs) – Repeated vs Non-repeated Tasks.

<!---- fig:rp13-qrt (leave a blank line before this) ------>








### Entropy of Query Reformulation Types {#sec-res-phase13-query-H}

<!----------- fig:rp13-qrt-entropy ----------->
```{r rp13-qrt-entropy, fig.scap='(ref:scap-rp13-qrt-entropy)', fig.cap = '(ref:cap-rp13-qrt-entropy)',  echo=FALSE, out.width='100%', fig.align='center'}
nbShowFig("figs/rp13-qrt-entropy")
```
<!-- each text reference needs to be their own single paragraph ! -->
(ref:cap-rp13-qrt-entropy) Entropy of Query Reformulation Types (QRTs) – Repeated vs Non-repeated Tasks.

(ref:scap-rp13-qrt-entropy) Entropy of Query Reformulation Types (QRTs) – Repeated vs Non-repeated Tasks.

<!---- fig:rp13-qrt-entropy (leave a blank line before this) ------>











## Number of Clicks per Query

<!----------- fig:rp13-query-click ----------->
```{r rp13-query-click, fig.scap='(ref:scap-rp13-query-click)', fig.cap = '(ref:cap-rp13-query-click)',  echo=FALSE, out.width='100%', fig.align='center'}
nbShowFig("figs/rp13-query-click")
```
<!-- each text reference needs to be their own single paragraph ! -->
(ref:cap-rp13-query-click) Number of Clicks Per Query – Repeated vs Non-repeated Tasks.

(ref:scap-rp13-query-click) Number of Clicks Per Query – Repeated vs Non-repeated Tasks.

<!---- fig:rp13-query-click (leave a blank line before this) ------>










## L vs I: Interaction with Search Results vs Content Pages

<!----------- fig:rp13-lvi ----------->
```{r rp13-lvi, fig.scap='(ref:scap-rp13-lvi)', fig.cap = '(ref:cap-rp13-lvi)',  echo=FALSE, out.width='100%', fig.align='center'}
nbShowFig("figs/rp13-lvi")
```
<!-- each text reference needs to be their own single paragraph ! -->
(ref:cap-rp13-lvi) Differences in interactions with search results vs. content pages - repeated and non-repeated tasks.

(ref:scap-rp13-lvi) Differences in interactions with search results vs. content pages - repeated and non-repeated tasks.

<!---- fig:rp13-lvi (leave a blank line before this) ------>









## Entropy of Search Tactic Sequences

<!----------- fig:rp13-tactic-entropy ----------->
```{r rp13-tactic-entropy, fig.scap='(ref:scap-rp13-tactic-entropy)', fig.cap = '(ref:cap-rp13-tactic-entropy)',  echo=FALSE, out.width='100%', fig.align='center'}
nbShowFig("figs/rp13-tactic-entropy")
```
<!-- each text reference needs to be their own single paragraph ! -->
(ref:cap-rp13-tactic-entropy) Entropy of Search Tactics – Repeated vs Non-repeated Tasks.

(ref:scap-rp13-tactic-entropy) Entropy of Search Tactics – Repeated vs Non-repeated Tasks.

<!---- fig:rp13-tactic-entropy (leave a blank line before this) ------>
