# `r metadata[['author']]`'s `r metadata[['document-type']]` {-}

Welcome to the eBook version of <a href="https://nilavra.in" target="_blank">`r metadata[['author']]`'s</a> `r metadata[['degree-suffix']]` `r metadata[['document-type']]`.
This website disseminates my PhD research in a format that is more user-friendly and accessible than a 150-page, double-spaced PDF file. 
<!-- The materials were submitted to the Graduate School of UT Austin on December 8, 2017 in fullfillment of the requirments for a Ph.D. degree. -->


If you are viewing this webpage on a laptop or tablet, you may be able to see the table of contents on the left, and the subheadings for each page on the right. If you are viewing this webpage on your phone, you can navigate between chapters by clicking the three horizontal bars in the top right to view the table of contents. 
To view a PDF version, click on the cover-sheet below.
Happy viewing! 😊

About the author, Nilavra Bhattacharya:
<a href="https://nilavra.in" target="_blank">https://nilavra.in</a>

<!-- To read this eBook, simply scroll down, or jump to a specific chapter from the navigation menu (on the left in dekstops; on the top in mobile devices). -->


<!-- - To view/download a PDF version of the thesis, click the button below. -->

<a href="_main.pdf" target="_blank" title="Click to view PDF version" class="text-decoration-none">
<div class="text-center shadow pt-1 pb-3 mb-5 bg-white rounded">
<div class="text-right pt-3 pb-2 px-4 small font-italic">Draft version: `r format(Sys.time(), '%Y-%m-%d %H:%M:%S')` CST</div>
<div style="font-weight:bold; line-height:2.5; max-width: 80%; margin: 0 auto; font-size:120%">`r metadata[['title']]`</div>
\
by
\
\
<span style="font-weight:bold;">`r metadata[['author']]`</span>
\
<span style="font-size:20px">`r metadata[['author-dispname']]`</span>
\
\
\
**`r metadata[['document-type']]`**
\
\
Presented to the `r metadata[['department']]` \
of `r metadata[['university']]`\
in Partial Fulfillment\
of the Requirements\
for the Degree of\
\
\
\
**`r metadata[['degree']]`**
\
\
`r metadata[['university']]`\
`r metadata[['degree-month']]` `r metadata[['degree-year']]`
</div>
<div style="margin-top: -35px; text-align: center; font-size:85%; color:#555"> Click on the coversheet to view a PDF version of this `r metadata[['document-type']]`.</div>
</a>


<!-- Uncomment the below lines to show button for PDF -->
<!-- 
<div class="d-flex justify-content-center">
<a href="_main.pdf" class="btn btn-primary " target="_blank">
View PDF Version of this Thesis
</a>
</div> 
-->



## Abstract {-}
```{r abstract, child=here::here('front-and-back-matter/_abstract-main.Rmd')}
```


## `r metadata[['abstract-second-language-heading']]` (Abstract in `r metadata[['second-language']]`) {-}
```{r abstract, child=here::here('front-and-back-matter/_abstract-second-language.Rmd')}
```


## Acknowledgments {-}
```{r acknowledgments, child=here::here('front-and-back-matter/_acknowledgements.Rmd')}
```


::::::::: {.byline}
Original Template:
[`oxforddown`](https://github.com/ulyngs/oxforddown) by Ulrik Lyngs, 
thesis template for [R Markdown](https://rmarkdown.rstudio.com)
:::::::::

Nilavra's Homepage:
<a href="https://nilavra.in" target="_blank">https://nilavra.in</a>
