# Nilavra Bhattacharya's PhD Thesis {-}



Welcome to the eBook version of my work-in-progress PhD dissertation.
To read the eBook version, simply scroll down, or jump to a specific chapter from the navigation menu (on the left in dekstops; on the top in mobile devices).
<!-- - To view/download a PDF version of the thesis, click the button below. -->

<a href="_main.pdf" target="_blank" title="Click to view PDF version of thesis" class="text-decoration-none">
<div class="text-center shadow pt-1 pb-3 mb-5 bg-white rounded">
<div class="text-right pt-3 pb-2 px-4 small font-italic">Last compiled on `r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`</div>
**LongSAL: A Longitudinal Search as Learning Study
\
\
With University Students**
\
\
\
by
\
\
**Nilavra Bhattacharya**
\
<span style="font-size:20px">নীলাভ্র ভট্টাচার্য্য</span>
\
\
\
**Dissertation**
\
\
Presented to the Faculty of the Graduate School of\
The University of Texas at Austin\
in Partial Fulfillment\
of the Requirements\
for the Degree of\
\
\
\
**Doctor of Philosophy**
\
\
The University of Texas at Austin\
May 2023
</div>
</a>

<!-- Uncomment the below lines to show button for PDF -->
<!-- 
<div class="d-flex justify-content-center">
<a href="_main.pdf" class="btn btn-primary " target="_blank">
View PDF Version of this Thesis
</a>
</div> 
-->



## Abstract {-}
```{r abstract, child=here::here('front-and-back-matter/_abstract.Rmd')}
```


## Acknowledgments {-}
```{r acknowledgments, child=here::here('front-and-back-matter/_acknowledgements.Rmd')}
```


::::::::: {.byline}
Original Template:
[`oxforddown`](https://github.com/ulyngs/oxforddown) by Ulrik Lyngs, 
thesis template for [R Markdown](https://rmarkdown.rstudio.com)
:::::::::