# [Work in progress] `r metadata[['author']]`'s `r metadata[['document-type']]` {-}

Welcome to the eBook version of `r metadata[['author']]`'s work-in-progress `r metadata[['degree-suffix']]` `r metadata[['document-type']]`.

To read this eBook, simply scroll down, or jump to a specific chapter from the navigation menu (on the left in dekstops; on the top in mobile devices).
To view a PDF version, click on the cover-sheet below.

<!-- - To view/download a PDF version of the thesis, click the button below. -->

<a href="_main.pdf" target="_blank" title="Click to view PDF version" class="text-decoration-none">
<div class="text-center shadow pt-1 pb-3 mb-5 bg-white rounded">
<div class="text-right pt-3 pb-2 px-4 small font-italic">Last compiled on `r format(Sys.time(), '%Y-%m-%d %H:%M:%S')` CST</div>
<div style="font-weight:bold; line-height:2.5; max-width: 80%; margin: 0 auto">`r metadata[['title']]`</div>
\
by
\
\
<span style="font-weight:bold;">`r metadata[['author']]`</span>
\
<span style="font-size:20px">`r metadata[['author-dispname']]`</span>
\
\
\
**`r metadata[['document-type']]`**
\
\
Presented to the `r metadata[['department']]` of\
`r metadata[['university']]`\
in Partial Fulfillment\
of the Requirements\
for the Degree of\
\
\
\
**`r metadata[['degree']]`**
\
\
`r metadata[['university']]`\
`r metadata[['degree-month']]` `r metadata[['degree-year']]`
</div>
<div style="margin-top: -35px; text-align: center; font-size:85%; color:#555"> Click on the coversheet to view a PDF version of this `r metadata[['document-type']]`.</div>
</a>


<!-- Uncomment the below lines to show button for PDF -->
<!-- 
<div class="d-flex justify-content-center">
<a href="_main.pdf" class="btn btn-primary " target="_blank">
View PDF Version of this Thesis
</a>
</div> 
-->



## Abstract {-}
```{r abstract, child=here::here('front-and-back-matter/_abstract.Rmd')}
```


## Acknowledgments {-}
```{r acknowledgments, child=here::here('front-and-back-matter/_acknowledgements.Rmd')}
```


::::::::: {.byline}
Original Template:
[`oxforddown`](https://github.com/ulyngs/oxforddown) by Ulrik Lyngs, 
thesis template for [R Markdown](https://rmarkdown.rstudio.com)
:::::::::